Is high social class always beneficial for survival? Adults and

### 2017-09-15 article2.Rmd
Change of title

---
title: Is high social class always beneficial for survival? A study of adults and
  elderly in Northern Sweden 1801--2013
author: Sören Edvinsson and Göran
  Broström
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
  bookdown::pdf_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
  bookdown::word_document2:
    toc: yes
    toc_depth: 2
    toc_float: yes
bibliography: mybib.bib
documentclass: article
citation-package: natbib
biblio-style: apalike
fontsize: 12pt
---

>>>>

---
title: Is high social class always beneficial for survival? Adults and
  elderly in Northern Sweden 1801--2013
author: Sören Edvinsson and Göran
  Broström
date: '`r Sys.Date()`'
output:
  bookdown::html_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
    toc_float: yes
  bookdown::pdf_document2:
    number_sections: yes
    toc: yes
    toc_depth: 2
  bookdown::word_document2:
    toc: yes
    toc_depth: 2
    toc_float: yes
bibliography: mybib.bib
documentclass: article
citation-package: natbib
biblio-style: apalike
fontsize: 12pt
---
